No sign of recovery

### 2018-05-23 Appendix_A.Rmd

---
title: "Appendix A"
output:
  bookdown::pdf_document2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

# Random communities {-}
```{r ransimfunctions}
# Number of simulations
nsim <- 100

# Function to sample community and callculate CM
getsamples <- function(s, nspec, d, EL) {
  sample(d %>% pull(paste(EL)), nspec, replace = FALSE) %>% mean(na.rm = TRUE)
}

# Prepare data from one site and calculate mean and CrI for sample and mean for real community
getsim <- function(x, EL, gain) {
  tt <- pl %>% filter(aID_STAO == x) %>% 
    group_by(aID_SP, T, F, N, L) %>% 
    dplyr::summarise(Occ1 = sum(Visit == 1),
                     Occ2 = sum(Visit == 2),
                     Occ3 = sum(Visit == 3))
  if(gain)  ausw <- (tt$Occ1 == 0 & tt$Occ2 == 1) | (tt$Occ2 == 0 & tt$Occ3 == 1)
  if(!gain) ausw <- (tt$Occ1 == 1 & tt$Occ2 == 0) | (tt$Occ2 == 1 & tt$Occ3 == 0)
  tmp <- map_dbl(1:nsim, getsamples, nspec = sum(ausw), d = tt, EL = EL)
  list(
    nchange = sum(ausw),
    meanreal = mean(tt[ausw, paste(EL)] %>% unlist, na.rm = TRUE),
    mean = mean(tmp, na.rm = TRUE),
    lower = quantile(tmp, probs = 0.05, na.rm = TRUE),
    upper = quantile(tmp, probs = 0.95, na.rm = TRUE))
}

# Function to prepare the res file for plotting
makesim <- function(EL, gain, sitem) {
  res <- tibble(aID_STAO = sites$aID_STAO, Sitemeasure = pull(sites[, paste(sitem)]))
  tmp <- map(res$aID_STAO, getsim, EL = EL, gain = gain)
  res$meanreal <- tmp %>% map_dbl("meanreal")
  res$mean <- tmp %>% map_dbl("mean")
  res$lower <- tmp %>% map_dbl("lower")
  res$upper <- tmp %>% map_dbl("upper")
  res
}
```

```{r Tplot, fig.cap="\\textit{Average Ellenberg value for \\textbf{temperature} of lost (A) and newly appearing (B) species compared to the same number of species that were randomly selected from all species recorded at the sample site (i.e. random communities). Crosses indicate the community mean of lost and newly appearing species; the grey vertical lines indicate the range of the 5\\% and 95\\% quantiles of community means calculated from the 1000 random communities for each site. The curves show the regression lines with third order polynomials for the community means of lost and newly appearing species (black solid lines) and for the average community means of random communities (orange dotted lines).}"}
# Make calculations and plot for Ellenberg T value
tres <- makesim(EL = "T", gain = FALSE, sitem = "Temperature")
txlab <- seq(0, 100, 10)
tylab <- seq(1, 5, 0.5)
ploss <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "orange", lty = 2) +
  scale_x_continuous(breaks = (txlab - 50) / 10, labels = txlab / 10, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1, 1)) +
  labs(x = "Annual mean temperature", y = "Ellenberg temperature value\n(community mean)",
       title = "(A) Species losses") 
tres <- makesim(EL = "T", gain = TRUE, sitem = "Temperature")
pgain <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "orange", lty = 2) +
  scale_x_continuous(breaks = (txlab - 50) / 10, labels = txlab/10, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1, 1)) +
  labs(x = "Annual mean temperature", y = "Ellenberg temperature value\n(community mean)",
       title = "(B) Species gains") 
multiplot(ploss, pgain, cols = 2)
```

@@

```{r Nplot, fig.cap="\\textit{Average Ellenberg value for \\textbf{nutrients} of lost (A) and newly appearing (B) species compared to the same number of species that were randomly selected from all species recorded at the sample site (i.e. random communities). Crosses indicate the community mean of lost and newly appearing species; the grey vertical lines indicate the range of the 5\\% and 95\\% quantiles of community means calculated from the 1000 random communities for each site. The curves show the regression lines with third order polynomials for the community means of lost and newly appearing species (black solid lines) and for the average community means of random communities (orange dotted lines).}"}
# Make calculations and plot for Ellenberg N value
tres <- makesim(EL = "N", gain = FALSE, sitem = "NTOT")
txlab <- seq(0, 40, 5)
tylab <- seq(1, 4, 0.5)
ploss <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "orange", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.2, 1)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(A) Species losses") 
tres <- makesim("N", gain = TRUE, sitem = "NTOT")
pgain <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "orange", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.2, 1)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(B) Species gains") 
multiplot(ploss, pgain, cols = 2)
```

>>>>

---
title: "Appendix A: Random community change"
toc: no
output:
  bookdown::pdf_document2
---

@@

# Introduction and mehtods {-}
Add text to explain the ideas and methods.

Auch noch auf Interaktion texten:
```{r}
library(arm)

res1 <- rbind(
  tres %>% transmute(aID_STAO = aID_STAO, Sitemeasure = Sitemeasure, mean = mean, type = "Sample"),
  tres %>% transmute(aID_STAO = aID_STAO, Sitemeasure = Sitemeasure, mean = meanreal, type = "Real"))
mod1 <- lmer(mean ~ Sitemeasure * type + (1|aID_STAO), data = res1)
mod2 <- lmer(mean ~ Sitemeasure + type + (1|aID_STAO), data = res1)
anova(mod1, mod2)

summary(glmer(SR ~ yr * NTOT + (yr|aID_STAO), data = surv, family = "poisson"))
mod1 <- lmer(N ~ yr * NTOT + (yr|aID_STAO), data = surv)
mod2 <- lmer(N ~ yr + NTOT + (yr|aID_STAO), data = surv)
anova(mod1, mod2)
```

# Results {-}

```{r Tplot, fig.cap="\\textit{Average Ellenberg value for \\textbf{temperature} of lost (A) and newly appearing (B) species compared to the same number of species that were randomly selected from all species recorded at the sample site (i.e. random communities). Crosses indicate the community mean of lost and newly appearing species; the grey vertical lines indicate the range of the 5\\% and 95\\% quantiles of community means calculated from the 1000 random communities for each site. The curves show the regression lines with third order polynomials for the community means of lost and newly appearing species (black solid lines) and for the average community means of random communities (orange dotted lines).}"}
# Make calculations and plot for Ellenberg T value
tres <- makesim(EL = "T", gain = FALSE, sitem = "Temperature")
txlab <- seq(0, 100, 10)
tylab <- seq(1, 5, 0.5)
ploss <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "orange", lty = 2) +
  scale_x_continuous(breaks = (txlab - 50) / 10, labels = txlab / 10, limits = c(-1, NA)) +
  scale_y_continuous(breaks = tylab, labels = tylab, limits = c(2, 4)) +
  labs(x = "Annual mean temperature", y = "Ellenberg temperature value\n(community mean)",
       title = "(A) Species losses") 
tres <- makesim(EL = "T", gain = TRUE, sitem = "Temperature")
pgain <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "orange", lty = 2) +
  scale_x_continuous(breaks = (txlab - 50) / 10, labels = txlab/10, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1, 1)) +
  labs(x = "Annual mean temperature", y = "Ellenberg temperature value\n(community mean)",
       title = "(B) Species gains") 
multiplot(ploss, pgain, cols = 2)
```

@@

```{r Nplot, fig.cap="\\textit{Average Ellenberg value for \\textbf{nutrients} of lost (A) and newly appearing (B) species compared to the same number of species that were randomly selected from all species recorded at the sample site (i.e. random communities). Crosses indicate the community mean of lost and newly appearing species; the grey vertical lines indicate the range of the 5\\% and 95\\% quantiles of community means calculated from the 1000 random communities for each site. The curves show the regression lines with third order polynomials for the community means of lost and newly appearing species (black solid lines) and for the average community means of random communities (orange dotted lines).}"}
# Make calculations and plot for Ellenberg N value
tres <- makesim(EL = "N", gain = FALSE, sitem = "NTOT")
txlab <- seq(0, 40, 5)
tylab <- seq(1, 4, 0.5)
ploss <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "orange", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.2, 1)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(A) Species losses") 
tres <- makesim("N", gain = TRUE, sitem = "NTOT")
pgain <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "orange", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = tylab, labels = tylab, limits = c(1.8, 4)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(B) Species gains") 
multiplot(ploss, pgain, cols = 2)
```

### 2018-05-23 Manuscript.Rmd

res[4, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$F, surv$Visit, mean), 2)
load("Modelfit/F-trend.RData")
res[4, "Trend"] <- fixef(mod)["yr"]
res[4, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[4, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

res[5, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$N, surv$Visit, mean), 2)
load("Modelfit/N-trend.RData")
res[5, "Trend"] <- fixef(mod)["yr"]
res[5, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[5, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

res[6, c("Period 1", "Period 2", "Period 3")] <- round(tapply(surv$L, surv$Visit, mean), 2)
load("Modelfit/L-trend.RData")
res[6, "Trend"] <- fixef(mod)["yr"]
res[6, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[6, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

@@

The different measures of total community structure suggested that plant communities in mountain hay meadows were stable between 2003 and 2017 (Table \@ref(communitytrends)): for each of the three 5-year survey periods the averages of alpha- and beta-diversity and the average Ellenberg values for temperature, nutrients, light and huminity did not vary much among the three sampling periods. Except for average Ellenberg value for temperature, the 90% credible-interval of the temporal trend contained zero and the probability of a trend $>0$ was rather close to 0.5.

```{r turnover}
load("Modelfit/turnover-trend.RData")
tmp <-  posterior_interval(mod, pars = "period")
CrI <- paste0(round(tmp[1,1], ndigits), " - ", round(tmp[1,2], ndigits))
```

The temporal stability as inferred from the community measures were, however, in contrast to the large  observed temporal turnover of recorded species. The average percentage $\pm$ SD of species that differed between the first and second survey at a site was `r mean(100 * sites$change1 / (sites$nochange1 + sites$change1))` $\pm$ `r sd(100 * sites$change1 / (sites$nochange1 + sites$change1))`% and the percentage of species that differ between the second and third survey was `r mean(100 * sites$change2 / (sites$nochange2 + sites$change2))` $\pm$ `r sd(100 * sites$change2 / (sites$nochange2 + sites$change2))`%. Thus, it seems that the turnover from the first/second survey to the temporal turnover of the second/third survey moderately decreased (90% Credible interval of the change in turnover estimated from a Binomial generalized linear model: `r CrI`).

```{r diffromrandom}
# Number of simulations
nsim <- 100

# Function to sample community and callculate CM
getsamples <- function(s, nspec, d, EL) {
  sample(d %>% pull(paste(EL)), nspec, replace = FALSE) %>% mean(na.rm = TRUE)
}

# Prepare data from one site and calculate mean and CrI for sample and mean for real community
getsim <- function(x, EL, gain) {
  tt <- pl %>% filter(aID_STAO == x) %>% 
    group_by(aID_SP, T, F, N, L) %>% 
    dplyr::summarise(Occ1 = sum(Visit == 1),
                     Occ2 = sum(Visit == 2),
                     Occ3 = sum(Visit == 3))
  if(gain)  ausw <- (tt$Occ1 == 0 & tt$Occ2 == 1) | (tt$Occ2 == 0 & tt$Occ3 == 1)
  if(!gain) ausw <- (tt$Occ1 == 1 & tt$Occ2 == 0) | (tt$Occ2 == 1 & tt$Occ3 == 0)
  tmp <- map_dbl(1:nsim, getsamples, nspec = sum(ausw), d = tt, EL = EL)
  list(
    nchange = sum(ausw),
    meanreal = mean(tt[ausw, paste(EL)] %>% unlist, na.rm = TRUE),
    mean = mean(tmp, na.rm = TRUE),
    lower = quantile(tmp, probs = 0.025, na.rm = TRUE),
    upper = quantile(tmp, probs = 0.975, na.rm = TRUE))
}

# Function to prepare the res file for plotting
makesim <- function(EL, gain) {
  res <- sites %>% 
    filter(NTOT < 4) %>% 
    transmute(aID_STAO = aID_STAO, Sitemeasure = NTOT)
  tmp <- map(res$aID_STAO, getsim, EL = EL, gain = gain)
  res$meanreal <- tmp %>% map_dbl("meanreal")
  res$mean <- tmp %>% map_dbl("mean")
  res$lower <- tmp %>% map_dbl("lower")
  res$upper <- tmp %>% map_dbl("upper")
  res
}

# Make calculations and plot for T value
tres <- makesim(EL = "T", gain = FALSE)

tres <- makesim("N", gain = TRUE)
txlab <- seq(0, 40, 5)
tylab <- seq(2, 4, 0.5)
pNgain <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey60", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.5, 1.5)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(B) Species gains") 
# Make calculations and plot for N value
tres <- makesim(EL = "N", gain = FALSE)
txlab <- seq(0, 40, 5)
tylab <- seq(2, 4, 0.5)
pNloss <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey60", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.5, 1.5)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(A) Species losses")

tres <- makesim("N", gain = TRUE)
txlab <- seq(0, 40, 5)
tylab <- seq(2, 4, 0.5)
pNgain <- ggplot(tres, aes(x = Sitemeasure, y = meanreal)) +
  geom_errorbar(aes(ymin = lower, ymax = upper), lwd = 0.5, colour = "grey80") +
  geom_point(shape = 4, colour = "black", cex = 2) +
  stat_smooth(method = "lm", formula = y ~ poly(x, 3), se = FALSE, col = "black") +
  stat_smooth(aes(y = mean), method = "lm", formula = y ~ poly(x,3), se = FALSE, col = "grey60", lty = 2) +
  scale_x_continuous(breaks = (txlab - 10) / 10, labels = txlab, limits = c(-1, NA)) +
  scale_y_continuous(breaks = (tylab - 3), labels = tylab, limits = c(-1.5, 1.5)) +
  labs(x = "Nitrogen deposition", y = "Ellenberg nutrient value\n(community mean)",
       title = "(B) Species gains")

res1 <- rbind(
  res %>% transmute(aID_STAO = aID_STAO, Sitemeasure = Sitemeasure, mean = mean, type = "Sample"),
  res %>% transmute(aID_STAO = aID_STAO, Sitemeasure = Sitemeasure, mean = meanreal, type = "Real"))
mod1 <- lmer(mean ~ Sitemeasure * type + (1|aID_STAO), data = res1)
mod2 <- lmer(mean ~ Sitemeasure + type + (1|aID_STAO), data = res1)
anova(mod1, mod2)

summary(glmer(SR ~ yr * NTOT + (yr|aID_STAO), data = surv, family = "poisson"))
mod1 <- lmer(N ~ yr * NTOT + (yr|aID_STAO), data = surv)
mod2 <- lmer(N ~ yr + NTOT + (yr|aID_STAO), data = surv)
anova(mod1, mod2)

@@

```{r, fig.cap="Noch einfügen."}
multiplot(pNloss, pNgain, cols = 2)
```

```{r compofvarianceran}
modcol <- summary(glmer(Occ ~ 1 + (1|aID_STAO) + (1|aID_SP), data = coldat, family = binomial))
modls <- summary(glmer(Occ ~ 1 + (1|aID_STAO) + (1|aID_SP), data = survdat, family = binomial))
getratio <- function(x) x[1] / x[2]
```

```{r compofvariance}
# Local survival
ref <- glmer(Occ ~ 1 + (1|aID_SP) + (1|aID_STAO), data = survdat, family = binomial)
modT <- glmer(Occ ~ Temperature * T + (1|aID_SP) + (1|aID_STAO), 
              data = survdat, family = binomial)
modF <- glmer(Occ ~ Precipitation * F + (1|aID_SP) + (1|aID_STAO), 
              data = survdat, family = binomial)
modN <- glmer(Occ ~ NTOT * N + (1|aID_SP) + (1|aID_STAO), 
              data = survdat, family = binomial)
modL <- glmer(Occ ~ Inclination * L + (1|aID_SP) + (1|aID_STAO), 
              data = survdat, family = binomial)
tt <- data.frame(anova(ref, modT, modF, modN, modL))
tt$Model <- c("Random change", "Temperature driven", "Precipitation driven", "Nitrogen driven", "Land-use driven")
tt <- tt[order(tt$AIC),]
tt$'Delta-AIC' <- tt$AIC - tt$AIC[1]
resls <- tt[, c("Model", "Df", "AIC", "Delta-AIC")]

# Colonization probability
ref <- glmer(Occ ~ 1 + (1|aID_SP) + (1|aID_STAO), data = coldat, family = binomial)
modT <- glmer(Occ ~ Temperature * T + (1|aID_SP) + (1|aID_STAO), 
              data = coldat, family = binomial)
modF <- glmer(Occ ~ Precipitation * F + (1|aID_SP) + (1|aID_STAO), 
              data = coldat, family = binomial)
modN <- glmer(Occ ~ NTOT * N + (1|aID_SP) + (1|aID_STAO), 
              data = coldat, family = binomial)
modL <- glmer(Occ ~ Inclination * L + (1|aID_SP) + (1|aID_STAO), 
              data = coldat, family = binomial)
tt <- data.frame(anova(ref, modT, modF, modN, modL))
tt$Model <- c("Random change", "Temperature driven", "Precipitation driven", "Nitrogen driven", "Land-use driven")
tt <- tt[order(tt$AIC),]
tt$'Delta-AIC' <- tt$AIC - tt$AIC[1]
rescol <- tt[, c("Model", "Df", "AIC", "Delta-AIC")]
```

```{r resdifeffects}
tt <- rbind(rescol, resls)
kable(tt, digits = 2, row.names = FALSE, format = "latex", caption = "Comparision of results from different drivers to explain colonization probability (a) and local survvival (b). See methods for the tested models.", booktabs = T) %>%
    kable_styling() %>%
    group_rows("(a) Colonization probability", 1, 5, bold = F, italic = T) %>%
    group_rows("(b) Local survival probability", 6, 10, bold = F, italic = T)
```

@@

```{r Teff, fig.cap="Colonization (a) and local survival (b) of low temperature species (Ellenberg T = 2; red line) and high temperature species (Ellengerg T = 4) species along the temperature gradient. Given are means and 95\\%-Credible Intervals from logistic linear mixed models."}
X <- seq(0, 10, 0.2)
Xsd <- (X - 5)

# Colonization
mod <- glmer(Occ ~ Temperature * T + (1|aID_SP) + (1|aID_STAO), data = coldat, family = binomial)
simdat <- arm::sim(mod, nsim)@fixef
post <- map(1:nsim, getposterior)
res <- rbind(compileres("EL = 2"), compileres("EL = 4"))
p1 <- ggplot(res, aes(x = X, y = mean, colour = value, shape = value)) +
  geom_ribbon(aes(ymin = low, ymax = high), fill = "black", col = "white", alpha = 0.2) +
  geom_line() +
    labs(title = "(a) Colonization", 
         y = "Colonization probability", 
         x = "Temperature gradient")

# Local survival
mod <- glmer(Occ ~ Temperature * T + (1|aID_SP) + (1|aID_STAO), data = survdat, family = binomial)
simdat <- arm::sim(mod, nsim)@fixef
post <- map(1:nsim, getposterior)
res <- rbind(compileres("EL = 2"), compileres("EL = 4"))
p2 <- ggplot(res, aes(x = X, y = mean, colour = value, shape = value)) +
  geom_ribbon(aes(ymin = low, ymax = high), fill = "black", col = "white", alpha = 0.2) +
  geom_line() +
    labs(title = "(b) Local survival", 
         y = "Local survival probability", 
         x = "Temperature gradient")
multiplot(p1, p2, cols = 2)
```

>>>>

res[4, c("Period 1", "Period 2", "Period 3")] <- tapply(surv$F, surv$Visit, mean)
load("Modelfit/F-trend.RData")
res[4, "Trend"] <- fixef(mod)["yr"]
res[4, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[4, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

res[5, c("Period 1", "Period 2", "Period 3")] <- tapply(surv$N, surv$Visit, mean)
load("Modelfit/N-trend.RData")
res[5, "Trend"] <- fixef(mod)["yr"]
res[5, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[5, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

res[6, c("Period 1", "Period 2", "Period 3")] <- tapply(surv$L, surv$Visit, mean)
load("Modelfit/L-trend.RData")
res[6, "Trend"] <- fixef(mod)["yr"]
res[6, c('5%', '95%')] <- posterior_interval(mod, pars = "yr")
res[6, 'Trend > 0'] <- mean(as.data.frame(mod, pars = "yr")$yr > 0)

@@

The different measures of total community structure suggested that plant communities in mountain hay meadows were rather stable between 2003 and 2017 and did not show a consistent increase or decrease over time (Table \@ref(communitytrends)): for each of the three 5-year survey periods the averages of alpha- and beta-diversity and the average Ellenberg values for temperature, nutrients, light and huminity did not vary much among the three sampling periods and the estimated trends were rather small. Except for average Ellenberg value for temperature, the 90% credible-interval of the temporal trend contained zero. The results from the linear mixed models suggest that a linear temporal change was most likely for the community mean of the Ellenberg value for temperature (probability for an increase: `r res[res$Measures == "Temperature value", "Trend > 0"]`), followed by the community mean of the Ellenberg light value (probaility for a decrease: `r 1 - res[res$Measures == "Light value", "Trend > 0"]`) and it was least likely for the alpha-diversity (probaility for an increase: `r res[res$Measures == "Alpha-diversity", "Trend > 0"]`). The chance that the community mean of the nutrient value decreased between 2003 and 2017 was `r 1- res[res$Measures == "Nutrients value", "Trend > 0"]`.

### Site perspecitve
```{r turnover}
# Load Binomial-GLMM for turnover
load("Modelfit/turnover-trend.RData")

# Calculate the probability of change
probchange <- as.data.frame(mod, pars = c("Temperature", "Precipitation", "NTOT", "Inclination")) %>% 
  apply(2, function(x) mean(x > 0))
decreasing <- fixef(mod)[c("Temperature", "Precipitation", "NTOT", "Inclination")] < 0
probchange[decreasing] <-  1 - probchange[decreasing]

# 90% CrI for period effect
tmp <-  posterior_interval(mod, pars = "period")
CrI <- paste0(round(tmp[1,1], ndigits), " - ", round(tmp[1,2], ndigits))

```
The temporal stability as inferred from the community measures were, however, in contrast to a rather large observed temporal turnover of recorded species. The average percentage $\pm$ SD of species that differed between the first and second survey at a site was `r mean(100 * sites$change1 / (sites$nochange1 + sites$change1))` $\pm$ `r sd(100 * sites$change1 / (sites$nochange1 + sites$change1))`% and the percentage of species that differ between the second and third survey was `r mean(100 * sites$change2 / (sites$nochange2 + sites$change2))` $\pm$ `r sd(100 * sites$change2 / (sites$nochange2 + sites$change2))`%. Thus, it seems that the turnover from the first/second survey to the turnover of the second/third survey moderately decreased (90% Credible interval of the change in turnover estimated from the Binomial generalized linear mixed model that also contained the site variables: `r CrI`).

### Species perspective
```{r}
# Get posteriors from all single species trend models
filenames <- list.files("SpeciesTrends", full.names = TRUE)
aID_SP <- str_split(list.files("SpeciesTrends"), "\\.") %>% map(1) %>% unlist
load(filenames[1])
posttrend <- array(NA, dim = c(length(trend), length(aID_SP)))
for(i in 1:length(filenames)){
  load(filenames[i])
  posttrend[, i] <- trend
}

# Get list of species for which trend estimates are available
spec <- pl %>% group_by(aID_SP, T, F, N, L) %>%
  dplyr::summarise(Nsites = n_distinct(aID_STAO),
                   Nrecords = n())
spec <- spec[!is.na(match(spec$aID_SP, aID_SP)), ]

# Function to calculate effect of Ellenberg values on trend
trendef <- function(x) {
  spec$Trend <- posttrend[x,]
  coef(lm(Trend ~ T + F + N + L, data = spec))
}

spec$Trend <- apply(posttrend, 2, median)
spec$TrendSD <- apply(posttrend, 2, sd)

summary(lm(Trend ~ T + F + N + L, data = spec, weights = 1/TrendSD))

library("nlme")		
vf <- varExp(form= ~ 1/TrendSD)		
gls(Trend ~ T + F + N + L, data = spec %>% filter(!is.na(T) & !is.na(F) & !is.na(N) & !is.na(L)), weights=vf) %>% summary

# Calculate for all samples of the posterior distribution
tt <- map(1:1000, trendef)
map_dbl(tt, "T") %>% quantile(probs = c(0.5, 0.05, 0.95))
map_dbl(tt, "F") %>% quantile(probs = c(0.5, 0.05, 0.95))
map_dbl(tt, "N") %>% quantile(probs = c(0.5, 0.05, 0.95))
map_dbl(tt, "L") %>% quantile(probs = c(0.5, 0.05, 0.95))

# Überlebenswahrscheinlichkeit ist grösser
glm(Occ ~ Temperature + Precipitation + NTOT + Inclination, data = survdat, family = binomial) %>% summary

# Einwanderwahrscheinlichkeit ist grösser
glm(Occ ~ Temperature + Precipitation + NTOT + Inclination, data = coldat, family = binomial) %>% summary

cbind(
survdat %>% group_by(T) %>% 
  dplyr::summarise(
    Anz_Ausgestroben = sum(Occ == 0)),
coldat %>% group_by(T) %>% 
  dplyr::summarise(
    N = n(),
    surv = mean(Occ)))

plot(tt$surv)

table(survdat$Period)

@@

--> Temperature and N have an effect on how species generally react.

Temporal turnover could be high due to random processes including

@@
